---
title: "SDS Project"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r install, echo = FALSE}
# Install required modules
# If not done yet, install the required modules, and load them.
# In particular, we need the WDI package. It downloads the requested data by using the World Bank's API, parses the resulting XML file, and formats it in long country-year format.
if(!require(WDI)){
  install.packages("WDI")
  library(WDI)
}

# install.packages("ggplot2")
library(ggplot2)

# install.packages("kableExtra")
library(kableExtra)

library(mediation)
library(tidyverse)
```

## List of countries of interest
We consider all European countries: Austria, Belgium, Bulgaria, Switzerland, Cyprus, Czech Republic, Germany, Denmark, Spain, Estonia, Finland, France, United Kingdom, Greece, Croatia, Hungary, Iceland, Italy, Lithuania, Luxembourg, Latvia, Malta, Netherlands, Norway, Poland, Portugal, Romania, Slovakia, Slovenia and Sweden. The ISO country codes can be searched from https://www.iban.com/country-codes.

```{r, echo=FALSE}
countries <- c("AT", # Austria
               "BE", # Belgium
               "BG", # Bulgaria
               "CH", # Switzerland
               "CY", # Cyprus
               "CZ", # Czech Republic
               "DE", # Germany
               "DK", # Denmark
               "ES", # Spain
               "EE", # Estonia
               "FI", # Finland
               "FR", # France
               "GB", # United Kingdom
               "GR", # Greece
               "HR", # Croatia
               "HU", # Hungary
               "IE", # Ireland
               "IT", # Italy
               "LT", # Lithuania
               "LU", # Luxembourg
               "LV", # Latvia
               "MT", # Malta
               "NL", # Netherlands 
               "PL", # Poland
               "PT", # Portugal
               "RO", # Romania
               "SK", # Slovakia
               "SI", # Slovenia
               "SE"  # Sweden
               )

# To do the analysis for a subset of the countries, edit and uncomment the following line 
# countries <- c("NL")
num_countries <- length(countries)
```

## Time period of interest
In order to keep the time period consistent between the world bank and the LinkedIn data, we choose the time period of interest from 2015 to 2019.
```{r, echo=FALSE}
start_year <- 2015
end_year <- 2019
num_years <- end_year - start_year + 1
num_datapoints <- num_countries * num_years
```

## Economic indicators of interest
For these indicators, we extract the data from the world bank interface. The entire list of indicators can be seen here: https://databank.worldbank.org/source/world-development-indicators.

First, we need the GDP per capita. This is the main variable of interest. For the analyses, we consider this as the dependent variable, and seek to understand the effect of various unemployment related parameters on the GDP per capita. There are several indicators of GDP per capital: constant 2010 US dollars, current US dollars, constant LCU, current LCU, etc. We use the GDP per capita in constant 2010 US dollars for our analysis.
```{r, echo=FALSE}
indicator_gdp_growth <- "NY.GDP.MKTP.KD.ZG"
indicator_gdp_per_capita <- "NY.GDP.PCAP.KD" # constant 2010 US$
# indicator_gdp_per_capita <- "NY.GDP.PCAP.CD" # GDP per capita (current US$)
# indicator_gdp_per_capita <- "NY.GDP.PCAP.KN" # GDP per capita (constant LCU)
# indicator_gdp_per_capita <- "NY.GDP.PCAP.CN" # GDP per capita (current LCU)
```

Among the unemployment indicators, we consider (i) the total unemployment percentage, (ii) the unemployment percentage in youths (ages 15-24), (iii) the unemployment percentage among males, and (iv) the unemployment percentage among females. In the world bank interface, for all these indicators, we have two estimates: (i) a national estimate and (ii) a modeled ILO estimate. For our analysis, we consider the national estimate.
```{r, echo=FALSE}
indicator_unemployment_total <- "SL.UEM.TOTL.NE.ZS" # Unemployment, total (% of total labor force) (national estimate)
indicator_unemployment_youth <- "SL.UEM.1524.NE.ZS" # Unemployment, youth total (% of total labor force ages 15-24) (national estimate)
indicator_unemployment_male <- "SL.UEM.TOTL.MA.NE.ZS" # Unemployment, male (% of male labor force) (national estimate)
indicator_unemployment_female <- "SL.UEM.TOTL.FE.NE.ZS" # Unemployment, female (% of female labor force) (national estimate)
```

Finally, we consider the division of the total employment in different industry sectors: namely (i) agriculture (consisting of activities in agriculture, hunting, forestry and fishing), (ii) industry (consisting of mining and quarrying, manufacturing, construction, and public utilities (electricity, gas, and water) and (iii) services (consisting of wholesale and retail trade and restaurants and hotels; transport, storage, and communications; financing, insurance, real estate, and business services; and community, social, and personal services). For these indicators, only one estimate (the modeled ILO estimate) is available, and we use the same.
```{r, echo=FALSE}
indicator_employment_agriculture <- "SL.AGR.EMPL.ZS" # Employment in agriculture (% of total employment) ()
indicator_employment_industry <- "SL.IND.EMPL.ZS" # Employment in industry (% of total employment) (modeled ILO estimate)
indicator_employment_services <- "SL.SRV.EMPL.ZS" # Employment in services (% of total employment)
```

## Correlation between total unemployment and GDP per capita (2015 - 2019)
```{r, echo=FALSE}
# load the GDP per capita
gdp_per_capita <- WDI(indicator = indicator_gdp_per_capita,
                      country = countries,
                      start = start_year,
                      end = end_year)

# load the total unemployment
unemployment <-  WDI(indicator = indicator_unemployment_total,
                     country = countries,
                     start = start_year,
                     end = end_year)
# The data is read from end_year to start_year for country[1], followed by end_year to start_year for country[2], and so on..
# Also, the countries are arranged in  the alphabetical order of their ISO codes! 
# For now, I have set ordered the values in the vector countries such that it remains the same after being read by WDI.

# Compute the correlation between the total unemployment and the GDP per capita
corr_gdp_unemployment <- cor(unemployment[,3], gdp_per_capita[,3])
corr_gdp_unemployment <- signif(corr_gdp_unemployment, 3)
```
The Pearson correlation coefficient between the total unemployment rate and the per capita GDP between 2015 and 2019 in European countries is `r corr_gdp_unemployment`.

```{r, fig.width = 5, fig.height = 5, echo=FALSE}
# Plot the GDP per capita vs the Unemployment rate  (for all countries and all years together)
plot(unemployment[,3],
     gdp_per_capita[,3],
     main="Europe, 2015-2019",
     xlab="Total unemployment %",
     ylab="GDP per capita (constant 2010 USD)",
     cex=0.5)
```

```{r permutation, echo=FALSE}
# Permutation test to compute the statistical significance of the correlation
# repeat shuffling for N times
N <- 10000 
# vector with the results of the test statistic under each permutation
corr_gdp_unemployment_permutation_test <- numeric(length = N) 
for(i in 1:N)
{
  unemployment_shufled <- unemployment[sample(nrow(unemployment)),]
  corr_gdp_unemployment_permutation_test[i] <- cor(unemployment_shufled[,3],
                                                   gdp_per_capita[,3])
}

# Computing the p-value of the permutation test
# A nice explanation of permutation test can be read here: https://www.jwilber.me/permutationtest/
# For testing the significance of a positive correlation, we need a >= in the formula below
# For testing the significance of a negative correlation, we need a <= in the formula below
p_value_Cor <- (sum(corr_gdp_unemployment_permutation_test<=corr_gdp_unemployment)+1)/length(corr_gdp_unemployment_permutation_test)
```
In order to check the statistical significance of the computed correlation, let's do a permutation analysis. Taking `r N` permutations, we find the p-value of the measured correlation to be `r p_value_Cor`. As the p-value is smaller than 0.05, the measured correlation is statistically significant.

```{r permutation_plot, echo=FALSE, fig.width = 5, fig.height = 5}
# Plotting the histogram of the computed correlation coefficients.
# Showing as a red line, the correlation coefficient between the unshuffled variables.
hist(corr_gdp_unemployment_permutation_test,
     xlim=range(c(corr_gdp_unemployment_permutation_test, corr_gdp_unemployment)),
     main="Permutation test",
     xlab="Correlation coefficient",
     cex=0.5)
abline(v=corr_gdp_unemployment, col="red")
```

```{r bootstrap, echo=FALSE}
# Bootstrapping to obtain an uncertainty on the correlation coefficient
# obtain M bootstrap samples and calculate the correlation coefficient every time
M <- 10000
corr_gdp_unemployment_bootstrap <- numeric(M)
for(i in 1:M)
{
  sampling_indices <- sample(seq(1, length(unemployment[,3]), by=1), size=num_datapoints, replace=TRUE)
  corr_gdp_unemployment_bootstrap[i] <- cor(unemployment[,3][sampling_indices], gdp_per_capita[,3][sampling_indices])
}

bt_mean <- signif(mean(corr_gdp_unemployment_bootstrap), 3)
bt_std <- signif(sd(corr_gdp_unemployment_bootstrap), 3)
bt_perc97 <- signif(quantile(corr_gdp_unemployment_bootstrap, probs=c(0.975)), 3)
bt_perc2 <- signif(quantile(corr_gdp_unemployment_bootstrap, probs=c(0.025)), 3)
```
Further, let's do a bootstrap analysis to quantify the uncertainty in the measured correlation value. Repeating the bootstrap analysis `r M` times, we find the mean correlation to be `r bt_mean`, with a standard deviation of `r bt_std`. Thus, although the measured coefficient is unbiased, there seems to relatively high uncertainty in the measurement. This shows the unreliability of the measured correlation, and indicates that the real correlation value for a larger data-set may be remarkably different.

```{r, fig.width = 5, fig.height = 5, echo=FALSE}
hist(corr_gdp_unemployment_bootstrap,
     main="Bootstrapping analysis",
     xlab="Correlation coefficient",
     cex=0.5)
abline(v=corr_gdp_unemployment, col="red")

# print(paste("The measured coefficient is ", signif(corr_gdp_unemployment, 3), sep=''))
# print(paste("And the mean of the bootstrapped coefficient is ", bt_mean, sep=''))
# print(paste("The standard deviation is ", bt_std, sep=''))
# paste("The 95% density interval goes from ", bt_perc97, " to ", bt_perc2, sep='')
```


## Yearwise analysis (2005 - 2019)
The substantial uncertainty in the measured correlation could be due to multiple reasons. It may indicate that the relationship between the GDP per capita and the total unemployment is complicated, and perhaps dependent on several other variables. Further, the cumulative analysis over the 5 year time period (2015 - 2019) may be further complicating the relationship by introducing additional variations that may have occurred in different countries in different years within the considered time period. In order to alleviate this complication, we study the relationship between the GDP per capita and the total unemployment for each year separately. As there is no dependency of this yearwise analysis on the LinkedIN analysis, and to benefit from the additional data available via the WDI interface, we include an extended time period: from 2005 to 2019.
```{r correlation_one_year, echo=FALSE}
years = c()
coefs = c()
btmeans = c()
btstd = c()
pvalues = c()

print("Year | Correlation | BT mean | BT std | p-value")

for (year in seq(from = 2005, to = 2019, by = 1))
{

  # load the GDP per capita
  gdp_per_capita <- WDI(indicator = indicator_gdp_per_capita,
                        country = countries,
                        start = year,
                        end = year)

  # load the total unemployment
  unemployment <-  WDI(indicator = indicator_unemployment_total,
                       country = countries,
                       start = year,
                       end = year)

  # Compute the correlation between the total unemployment and the GDP per capita
  corr_gdp_unemployment_this_year <- signif(cor(unemployment[,3], gdp_per_capita[,3]), 3)
  
  # permutation test for this year
  N <- 10000 
  # vector with the results of the test statistic under each permutation
  corr_gdp_unemployment_permutation_test <- numeric(length = N) 
  for(i in 1:N)
  {
    unemployment_shufled <- unemployment[sample(nrow(unemployment)),]
    corr_gdp_unemployment_permutation_test[i] <- cor(unemployment_shufled[,3],
                                                     gdp_per_capita[,3])
  }
  p_value_Cor <- (sum(corr_gdp_unemployment_permutation_test<=corr_gdp_unemployment_this_year)+1)/length(corr_gdp_unemployment_permutation_test)
  
  # bootstrap analysis for this year
  M <- 10000
  corr_gdp_unemployment_bootstrap <- numeric(M)
  for(i in 1:M)
  {
    sampling_indices <- sample(seq(1, length(unemployment[,3]), by=1), size=num_countries, replace=TRUE)
    corr_gdp_unemployment_bootstrap[i] <- cor(unemployment[,3][sampling_indices], gdp_per_capita[,3][sampling_indices])
  }
  bt_mean <- signif(mean(corr_gdp_unemployment_bootstrap), 3)
  bt_std <- signif(sd(corr_gdp_unemployment_bootstrap), 3)

  print(paste(year, corr_gdp_unemployment_this_year, bt_mean, bt_std, p_value_Cor))
  
  years <- append(years, year)
  coefs <- append(coefs, corr_gdp_unemployment_this_year)
  btmeans <- append(btmeans, bt_mean)
  btstd <- append(btstd, bt_std)
  pvalues <- append(pvalues, p_value_Cor)
  
}

qplot(years, coefs) + geom_errorbar(aes(x=years, ymin=coefs-btstd, ymax=coefs+btstd), width=0.25) + ggtitle("Longitudinal analysis") + xlab("Year") + ylab("Correlation coefficient")
```

We observe a clear trend in the yearwise analysis: the  correlation between the total unemployment and the GDP per capita becomes consistently weaker from 2010 to 2019. The error bars in the plot above indicate the standard deviation values computed via bootstrapping. Further, permutation testing shows that the correlation values before 2016 are statistically significant, while the ones from 2016 are not.

Based on this analysis, we conclude that there may be several time-dependent factors affecting the relationship between the GDP per capita and the total unemployment. A multivariate analysis including such additional factors is outside the scope of this project. Accordingly, we decide to focus on a single year for the further analysis. As the correlation is statistically significant before 2016, and we have LinkedIn data available from 2015 onwards, 2015 is the only year which matches both our analysis criteria. 

```{r, echo=FALSE}
compute_correlation <- function(indc_gdp, indc_employ, countries, year)
{
  
  gdp_per_capita <- WDI(indicator = indc_gdp, country = countries, start = year, end = year) # load the GDP per capita
  unemployment <-  WDI(indicator = indc_employ, country = countries, start = year, end = year) # load the total unemployment
  corr <- signif(cor(unemployment[,3], gdp_per_capita[,3]), 3) # Compute correlation
  
  # Permutation test to compute the statistical significance of the correlation
  N <- 10000
  corr_perm_test <- numeric(length = N) 
  for(i in 1:N)
  {
    unemployment_shufled <- unemployment[sample(nrow(unemployment)),]
    corr_perm_test[i] <- cor(unemployment_shufled[,3], gdp_per_capita[,3])
  }
  p_value <- signif((sum(corr_perm_test<=corr)+1)/length(corr_perm_test), 3)
  
  # Bootstrapping to obtain an uncertainty on the correlation coefficient
  M <- 10000
  corr_bootstrap <- numeric(M)
  for(i in 1:M)
  {
    sampling_indices <- sample(seq(1, length(unemployment[,3]), by=1), size=num_datapoints, replace=TRUE)
    corr_bootstrap[i] <- cor(unemployment[,3][sampling_indices], gdp_per_capita[,3][sampling_indices])
  }
  bt_mean <- signif(mean(corr_bootstrap), 3)
  bt_std <- signif(sd(corr_bootstrap), 3)

  cor_list <- list("year" = year, "coef" = corr, "btmean" = bt_mean, "btstd" = bt_std, "p" = p_value)
  
  return(cor_list)
}
```

## Group Analysis (2015)
The table below shows the correlation values for different sub-groups in the population. It can be seen that the correlation values are quite similar for all the considered groups.
```{r group_analysis, echo=FALSE}
cor_total <- compute_correlation(indicator_gdp_per_capita, indicator_unemployment_total, countries, 2015)
cor_youth <- compute_correlation(indicator_gdp_per_capita, indicator_unemployment_youth, countries, 2015)
cor_male <- compute_correlation(indicator_gdp_per_capita, indicator_unemployment_male, countries, 2015)
cor_female <- compute_correlation(indicator_gdp_per_capita, indicator_unemployment_female, countries, 2015)

group_coefs <- c(cor_total$coef, cor_youth$coef, cor_male$coef, cor_female$coef)
group_btmean <- c(cor_total$btmean, cor_youth$btmean, cor_male$btmean, cor_female$btmean)
group_btstd <- c(cor_total$btstd, cor_youth$btstd, cor_male$btstd, cor_female$btstd)
group_pvalues <- c(cor_total$p, cor_youth$p, cor_male$p, cor_female$p)
correlation_group_analysis <- data.frame(group_coefs, group_btmean, group_btstd, group_pvalues)

rownames(correlation_group_analysis) <- c("Total", "Youth", "Male", "Female")
kable(correlation_group_analysis,  col.names = c("Correlation",
                                                 "Bootstrapping mean",
                                                 "Bootstrapping std. dev.",
                                                 "P-value")) %>% kable_material(c("striped", "hover"))
```


## Mediation Analysis (2015)

# Dataframe merging
```{r mediation_analysis, echo=FALSE}

unemployment_youth <-  WDI(indicator = indicator_unemployment_youth,
                     country = countries,
                     start = start_year,
                     end = end_year)
unemployment_male <-  WDI(indicator = indicator_unemployment_male,
                     country = countries,
                     start = start_year,
                     end = end_year)
unemployment_female <-  WDI(indicator = indicator_unemployment_female,
                     country = countries,
                     start = start_year,
                     end = end_year)
employment_agr <-  WDI(indicator = indicator_employment_agriculture,
                     country = countries,
                     start = start_year,
                     end = end_year)
employment_industry <-  WDI(indicator = indicator_employment_industry,
                     country = countries,
                     start = start_year,
                     end = end_year)
employment_services <-  WDI(indicator = indicator_employment_services,
                     country = countries,
                     start = start_year,
                     end = end_year)



onedf <- merge(gdp_per_capita, unemployment)
onedf <- merge(merge(merge(merge(merge(merge(onedf, unemployment_youth), unemployment_female), unemployment_male), employment_agr), employment_industry), employment_services)

onedf <- onedf %>% 
  rename(
     unemployment = SL.UEM.TOTL.NE.ZS,
     gdp_per_capita = NY.GDP.PCAP.KD,
     unemployment_youth = SL.UEM.1524.NE.ZS,
     unemployment_male = SL.UEM.TOTL.MA.NE.ZS,
     unemployment_female = SL.UEM.TOTL.FE.NE.ZS,
     employment_agr = SL.AGR.EMPL.ZS,
     employment_industry = SL.IND.EMPL.ZS,
     employment_services = SL.SRV.EMPL.ZS
    )

onedf_filt <- filter(onedf, year>=2015)
```


# Mediation analysis (GDP, unemp_youth, empl_agr)

```{r mediation_analysis, echo=FALSE}
agr_dep_var <- onedf_filt$gdp
agr_indep_var <- onedf_filt$employment_agr
agr_indep_var_fem <- onedf_filt$employment_agr
agr_mediator <- onedf_filt$unemployment_youth
agr_mediator_fem <- onedf_filt$unemployment_female

agr_df_mediation <- data.frame(agr_indep_var,agr_mediator,agr_dep_var)
agr_df_mediation_fem <- data.frame(agr_indep_var_fem,agr_mediator_fem,agr_dep_var)

agr.totaleffect=lm(agr_dep_var~agr_indep_var, agr_df_mediation)
summary(agr.totaleffect)

agr.totaleffect_fem=lm(agr_dep_var~agr_indep_var_fem, agr_df_mediation_fem)
summary(agr.totaleffect_fem)

agr.agr_mediator=lm(agr_mediator~agr_indep_var,agr_df_mediation)
summary(agr.agr_mediator)

agr.agr_mediator_fem=lm(agr_mediator_fem~agr_indep_var_fem,agr_df_mediation_fem)
summary(agr.agr_mediator_fem)

agr.dv=lm(agr_dep_var~agr_indep_var+agr_mediator,agr_df_mediation)
summary(agr.dv)

agr.dv_fem=lm(agr_dep_var~agr_indep_var_fem+agr_mediator_fem,agr_df_mediation_fem)
summary(agr.dv_fem)

agr_results = mediate(agr.agr_mediator, agr.dv, treat='agr_indep_var', mediator='agr_mediator', boot=T)
summary(agr_results)

agr_results_fem = mediate(agr.agr_mediator_fem, agr.dv_fem, treat='agr_indep_var_fem', mediator='agr_mediator_fem', boot=T)
summary(agr_results_fem)


plot(agr_indep_var, agr_dep_var)


agr_group_tot <- c(agr.totaleffect$coefficients[2],agr.totaleffect_fem$coefficients[2])
agr_group_tot_p <- c(summary(agr.totaleffect)$coefficients[2,4], summary(agr.totaleffect_fem)$coefficients[2,4])
agr_group_mediator <- c(agr.agr_mediator$coefficients[2],agr.agr_mediator_fem$coefficients[2])
agr_group_mediator_p <- c(summary(agr.agr_mediator)$coefficients[2,4], summary(agr.agr_mediator_fem)$coefficients[2,4])
agr_group_dv <- c(agr.dv$coefficients[2],agr.dv_fem$coefficients[2])
agr_group_dv_p <- c(summary(agr.dv)$coefficients[2,4], summary(agr.dv_fem)$coefficients[2,4])

agr_group_analysis <- data.frame(agr_group_tot,agr_group_tot_p, agr_group_mediator, agr_group_mediator_p, agr_group_dv, agr_group_dv_p)
rownames(agr_group_analysis) <- c("Youth", "Female")
kable(agr_group_analysis,  col.names = c("I->D",
                                         "p-value",
                                         "I->M",
                                         "p-value",
                                         "I+M->D",
                                         "p-value")) %>% kable_material(c("striped", "hover"))

```

# Mediation analysis (GDP, unemp_youth, empl_ind)
```{r}

# ==========================================
# Mediation 
# ==========================================
ind_dep_var <- onedf_filt$gdp
ind_indep_var <- onedf_filt$employment_industry
ind_indep_var_fem <- onedf_filt$employment_industry
ind_mediator <- onedf_filt$unemployment_youth
ind_mediator_fem <- onedf_filt$unemployment_female

ind_df_mediation <- data.frame(ind_indep_var,ind_mediator,ind_dep_var)
ind_df_mediation_fem <- data.frame(ind_indep_var_fem,ind_mediator_fem,ind_dep_var)

ind.totaleffect=lm(ind_dep_var~ind_indep_var, ind_df_mediation)
summary(ind.totaleffect)

ind.totaleffect_fem=lm(ind_dep_var~ind_indep_var_fem, ind_df_mediation_fem)
summary(ind.totaleffect_fem)

ind.ind_mediator=lm(ind_mediator~ind_indep_var,ind_df_mediation)
summary(ind.ind_mediator)

ind.ind_mediator_fem=lm(ind_mediator_fem~ind_indep_var_fem,ind_df_mediation_fem)
summary(ind.ind_mediator_fem)

ind.dv=lm(ind_dep_var~ind_indep_var+ind_mediator,ind_df_mediation)
summary(ind.dv)

ind.dv_fem=lm(ind_dep_var~ind_indep_var_fem+ind_mediator_fem,ind_df_mediation_fem)
summary(ind.dv_fem)

ind_results = mediate(ind.ind_mediator, ind.dv, treat='ind_indep_var', mediator='ind_mediator', boot=T)
summary(ind_results)

ind_results_fem = mediate(ind.ind_mediator_fem, ind.dv_fem, treat='ind_indep_var_fem', mediator='ind_mediator_fem', boot=T)
summary(ind_results_fem)



plot(ind_indep_var, ind_dep_var)

ind_group_tot <- c(ind.totaleffect$coefficients[2],ind.totaleffect_fem$coefficients[2])
ind_group_tot_p <- c(summary(ind.totaleffect)$coefficients[2,4], summary(ind.totaleffect_fem)$coefficients[2,4])
ind_group_mediator <- c(ind.ind_mediator$coefficients[2],ind.ind_mediator_fem$coefficients[2])
ind_group_mediator_p <- c(summary(ind.ind_mediator)$coefficients[2,4], summary(ind.ind_mediator_fem)$coefficients[2,4])
ind_group_dv <- c(ind.dv$coefficients[2],ind.dv_fem$coefficients[2])
ind_group_dv_p <- c(summary(ind.dv)$coefficients[2,4], summary(ind.dv_fem)$coefficients[2,4])

ind_group_analysis <- data.frame(ind_group_tot,ind_group_tot_p, ind_group_mediator, ind_group_mediator_p, ind_group_dv, ind_group_dv_p)
rownames(ind_group_analysis) <- c("Youth", "Female")
kable(ind_group_analysis,  col.names = c("I->D",
                                         "p-value",
                                         "I->M",
                                         "p-value",
                                         "I+M->D",
                                         "p-value")) %>% kable_material(c("striped", "hover"))


```

# Mediation analysis (GDP, unemp_youth, empl_services)
```{r}

ser_dep_var <- onedf_filt$gdp
ser_indep_var <- onedf_filt$employment_services
ser_indep_var_fem <- onedf_filt$employment_services
ser_mediator <- onedf_filt$unemployment_youth
ser_mediator_fem <- onedf_filt$unemployment_female

ser_df_mediation <- data.frame(ser_indep_var,ser_mediator,ser_dep_var)
ser_df_mediation_fem <- data.frame(ser_indep_var_fem,ser_mediator_fem,ser_dep_var)

ser.totaleffect=lm(ser_dep_var~ser_indep_var, ser_df_mediation)
summary(ser.totaleffect)

ser.totaleffect_fem=lm(ser_dep_var~ser_indep_var_fem, ser_df_mediation_fem)
summary(ser.totaleffect_fem)

ser.ser_mediator=lm(ser_mediator~ser_indep_var,ser_df_mediation)
summary(ser.ser_mediator)

ser.ser_mediator_fem=lm(ser_mediator_fem~ser_indep_var_fem,ser_df_mediation_fem)
summary(ser.ser_mediator_fem)

ser.dv=lm(ser_dep_var~ser_indep_var+ser_mediator,ser_df_mediation)
summary(ser.dv)

ser.dv_fem=lm(ser_dep_var~ser_indep_var_fem+ser_mediator_fem,ser_df_mediation_fem)
summary(ser.dv_fem)

ser_results = mediate(ser.ser_mediator, ser.dv, treat='ser_indep_var', mediator='ser_mediator', boot=T)
summary(ser_results)

ser_results_fem = mediate(ser.ser_mediator_fem, ser.dv_fem, treat='ser_indep_var_fem', mediator='ser_mediator_fem', boot=T)
summary(ser_results_fem)



plot(ser_indep_var, ser_dep_var)


ser_group_tot <- c(ser.totaleffect$coefficients[2],ser.totaleffect_fem$coefficients[2])
ser_group_tot_p <- c(summary(ser.totaleffect)$coefficients[2,4], summary(ser.totaleffect_fem)$coefficients[2,4])
ser_group_mediator <- c(ser.ser_mediator$coefficients[2],ser.ser_mediator_fem$coefficients[2])
ser_group_mediator_p <- c(summary(ser.ser_mediator)$coefficients[2,4], summary(ser.ser_mediator_fem)$coefficients[2,4])
ser_group_dv <- c(ser.dv$coefficients[2],ser.dv_fem$coefficients[2])
ser_group_dv_p <- c(summary(ser.dv)$coefficients[2,4], summary(ser.dv_fem)$coefficients[2,4])

ser_group_analysis <- data.frame(ser_group_tot,ser_group_tot_p, ser_group_mediator, ser_group_mediator_p, ser_group_dv, ser_group_dv_p)
rownames(ser_group_analysis) <- c("Youth", "Female")
kable(ser_group_analysis,  col.names = c("I->D",
                                         "p-value",
                                         "I->M",
                                         "p-value",
                                         "I+M->D",
                                         "p-value")) %>% kable_material(c("striped", "hover"))

```


## Sector Analysis with WDI data (2015)
In the remaining part of the project, we consider the effect of different employment sectors on the GDP. The table below shows the correlation values for different employment sectors. It can be seen that employment in agriculture and industry is negatively correlated with GDP per capita, while employment in services is positively correlated with the GDP per capita.
```{r sector_analysis, echo=FALSE}
cor_agri <- compute_correlation(indicator_gdp_per_capita, indicator_employment_agriculture, countries, 2015)
cor_indus <- compute_correlation(indicator_gdp_per_capita, indicator_employment_industry, countries, 2015)
cor_serv <- compute_correlation(indicator_gdp_per_capita, indicator_employment_services, countries, 2015)

sector_coefs <- c(cor_agri$coef, cor_indus$coef, cor_serv$coef)
sector_btmean <- c(cor_agri$btmean, cor_indus$btmean, cor_serv$btmean)
sector_btstd <- c(cor_agri$btstd, cor_indus$btstd, cor_serv$btstd)
sector_pvalues <- c(cor_agri$p, cor_indus$p, cor_serv$p)
correlation_sector_analysis <- data.frame(sector_coefs, sector_btmean, sector_btstd, sector_pvalues)

rownames(correlation_sector_analysis) <- c("Agriculture", "Industry", "Services")
kable(correlation_sector_analysis,  col.names = c("Correlation",
                                                 "Bootstrapping mean",
                                                 "Bootstrapping std. dev.",
                                                 "P-value")) %>% kable_material(c("striped", "hover"))

```

## Sector Analysis with LinkedIN data (2015)
```{r linkedin_analysis, echo=FALSE}

```

